---
title: "Phase III Trial Summary for Novel Oncology Agent (Drug X)"
author: "Your Name"
format: 
  html:
    code-fold: true
    code-summary: "Show code"
    embed-resources: true
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(gt)

demographics <- tribble(
  ~Characteristic, ~`Drug X + SOC (N=245)`, ~`Placebo + SOC (N=248)`, ~P_Value,
  "Age, Median (Range)", "65 (42-88)", "64 (41-89)", "0.52",
  "Sex: Male, n (%)", "130 (53.1)", "135 (54.4)", "0.78",
  "ECOG PS 0-1, n (%)", "230 (93.9)", "233 (94.0)", "0.99"
)

data_summary <- tibble(
  group = c("Drug X + SOC", "Placebo + SOC"),
  n_patients = c(245, 248),
  obj_response_rate = c(62.3, 31.5), # Objective Response Rate (ORR, %)
  or_ci_low = c(56.1, 25.8),
  or_ci_high = c(68.1, 37.5),
  p_value_orr = c(0.00001, NA), # p-value for ORR
  median_os_months = c(18.5, 12.1), # Median Overall Survival (OS, months)
  os_ci_low = c(16.9, 10.5),
  os_ci_high = c(20.3, 13.8),
  hr_os = c(0.65, NA), # Hazard Ratio for OS
  p_value_os = c(0.003, NA), # p-value for OS
  grade3_4_ae = c(28.4, 15.5) # Grade 3/4 Treatment-Related Adverse Events (%)
)
```

::: {.callout-important}

## Key Findings at a Glance

The results confirm the efficacy hypothesis: Drug X achieved superior response and survival outcomes with a statistically significant p-value for Overall Survival (p = `r data_summary %>% slice_head(n = 1) %>% pull(p_value_os)`) and a favorable Hazard Ratio (`r data_summary %>% slice_head(n = 1) %>% pull(hr_os)`).

:::

## 1. Baseline Patient Demographics

A balanced baseline demographic distribution is critical for a valid clinical trial. This section confirms the successful randomization process by showing key patient characteristics across the treatment arms.

```{r}
#| label: tbl-demographics
#| tbl-cap: "Baseline Demographics (Intent-to-Treat Population)"

gt(
  demographics,
  caption = "Baseline Demographics (Intent-to-Treat Population)"
)
```

The high p-values ($> 0.5$) confirm that there are no statistically significant differences in baseline characteristics between the two arms, supporting a fair comparison of treatment effects.

## 2. Primary Efficacy and Core Safety Data

This section contains the core analysis of the trial, focusing on the primary efficacy endpoints (ORR and OS) and the incidence of high-grade Adverse Events (AEs).

```{r}
#| label: tbl-results
#| tbl-cap: "Primary and Key Secondary Endpoint Summary: Drug X vs. Placebo (ITT Population)"
#| message: false
format_p_value <- function(p) {
  if (is.na(p)) {
    "-"
  } else if (p < 0.0001) {
    "< 0.0001"
  } else {
    formatC(p, digits = 3, format = "f")
  }
}

data_summary <- data_summary %>%
  mutate(
    ORR_CI = sprintf("%.1f (%.1f, %.1f)", obj_response_rate, or_ci_low, or_ci_high),
    Median_OS_CI = sprintf("%.2f (%.2f, %.2f)", median_os_months, os_ci_low, os_ci_high),
    p_value_orr_fmt = map_chr(p_value_orr, format_p_value),
    p_value_os_fmt  = map_chr(p_value_os,  format_p_value),
    HR_OS = if_else(is.na(hr_os), "-", sprintf("%.2f", hr_os)),
    Grade3_4_AE = sprintf("%.1f", grade3_4_ae)
  ) %>%
  select(
    `Treatment Arm` = group,
    N = n_patients,
    `ORR (%) [95% CI]` = ORR_CI,
    `p-value (ORR)` = p_value_orr_fmt,
    `Median OS (Months) [95% CI]` = Median_OS_CI,
    `HR (OS)` = HR_OS,
    `p-value (OS)` = p_value_os_fmt,
    `Grade 3/4 AEs (%)` = Grade3_4_AE
  )

gt(
  data_summary,
  caption = "Primary and Key Secondary Endpoint Summary: Drug X vs. Placebo (ITT Population)",
)
```

The results confirm the efficacy hypothesis: Drug X achieved superior response and survival outcomes with a statistically significant p-value for Overall Survival ($p=3.0 \times 10^{-3}$) and a favorable Hazard Ratio (0.65).

## 3. Safety Analysis: Visualization of Common Adverse Events (AEs)

While the previous section covered high-grade AEs, this ggplot2 visualization highlights the incidence of the most common AEs (all grades, incidence $>10\%$) to provide a comprehensive view of the treatment's common side effects.

```{r}
#| label: fig-safety
#| fig-cap: "Incidence of Common Adverse Events (All Grades, >10%)"
#| message: false

# Create Mock AE Incidence Data
ae_data <- tribble(
  ~AE, ~`Drug X + SOC`, ~`Placebo + SOC`,
  "Nausea", 45, 22,
  "Fatigue", 48, 30,
  "Diarrhea", 35, 15,
  "Anemia", 20, 18,
  "Rash", 30, 5,
  "Headache", 15, 12
)

# Reshape data for ggplot
ae_data_long <- ae_data %>%
  tidyr::pivot_longer(
    cols = -AE,
    names_to = "Arm",
    values_to = "Incidence_Percent"
  ) %>%
  mutate(
    Arm = factor(Arm, levels = c("Drug X + SOC", "Placebo + SOC"))
  )

# Plotting the AE Incidence
ggplot(ae_data_long, aes(x = AE, y = Incidence_Percent, fill = Arm)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  geom_text(
    aes(label = paste0(Incidence_Percent, "%")),
    position = position_dodge(width = 0.8),
    vjust = -0.5,
    size = 3.5,
    color = "black"
  ) +
  labs(
    y = "Incidence (%)",
    x = "",
    fill = "Treatment Arm"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.major.x = element_blank(),
    legend.position = "bottom"
  ) +
  scale_fill_manual(values = c("Drug X + SOC" = "#008000", "Placebo + SOC" = "#A9A9A9")) +
  ylim(0, 60)
```
